Pipit: Reactive Systems in \fstar ~(Extended Abstract)

### 2023-05-03 2023pipit/Main.tex
remove prim ty

\begin{tabbing}
  @MM@\= @let @\= \kill
  @let@ veh\_speed\_estimate $\omega_F$ $\omega_R$ $a_z$ = \\
    \> @let@ $v_F$ = $\omega_F \cdot $ circumference @in@ \\
    \> @let@ $v_R$ = $\omega_R \cdot $ circumference @in@ \\
    \\
    \> @let rec@ $\floor{\hat{v}}$ = @if@ $v_F \approx_\epsilon v_R$ \\
    \> \> @then@ $\min v_F v_R$ \\
    \> \> @else@ $(\xthen{\min v_F v_R}{\xfby{0}{\floor{\hat{v}}}}) + a_z - \epsilon$ @in@ \\
    \> @let rec@ $\ceil{\hat{v}}$ = @if@ $v_F \approx_\epsilon v_R$ \\
    \> \> @then@ $\max v_F v_R$ \\
    \> \> @else@ $(\xthen{\max v_F v_R}{\xfby{0}{\ceil{\hat{v}}}}) + a_z + \epsilon$ @in@
    \\
    \> $(\floor{\hat{v}}, \ceil{\hat{v}})$
\end{tabbing}

@@

The typing rules of Pipit are defined in \autoref{f:core-typing}, with the judgment form $\typing{\Gamma}{e}{\tau}$ that checks expression $e$ under streaming context $\Gamma$.
The grammar of types (\autoref{f:core-grammar}) distinguishes between bounded-size primitive types ($\primty$) and potentially higher-order types ($\tau$), which allows us to restrict streaming operations to only require bounded buffers.
\TODO{Not sure if this restriction is useful, as arbitrary functions can still use however much memory and time as they want.}

>>>>

\begin{tabbing}
  @MM@\= @let @\= \kill
  @let@ veh\_speed\_estimate $\omega_F$ $\omega_R$ $a_z$ = \\
    \> @let@ $v_F$ = $\omega_F \cdot $ circumference @in@ \\
    \> @let@ $v_R$ = $\omega_R \cdot $ circumference @in@ \\
    \\
    \> @let rec@ $\floor{\hat{v}}$ = @if@ $v_F \approx_\epsilon v_R$ \\
    \> \> @then@ $\min v_F v_R$ \\
    \> \> @else@ $(\xthen{\min v_F v_R}{\xfby{0}{\floor{\hat{v}}}}) + a_z - \epsilon$ @in@ \\
    \> @let rec@ $\ceil{\hat{v}}$ = @if@ $v_F \approx_\epsilon v_R$ \\
    \> \> @then@ $\max v_F v_R$ \\
    \> \> @else@ $(\xthen{\max v_F v_R}{\xfby{0}{\ceil{\hat{v}}}}) + a_z + \epsilon$ @in@ \\
    \\
    \> $(\floor{\hat{v}}, \ceil{\hat{v}})$
\end{tabbing}

@@

The typing rules of Pipit are defined in \autoref{f:core-typing}, with the judgment form $\typing{\Gamma}{e}{\tau}$ that checks expression $e$ under streaming context $\Gamma$.
% The grammar of types (\autoref{f:core-grammar}) distinguishes between bounded-size primitive types ($\primty$) and potentially higher-order types ($\tau$), which allows us to restrict streaming operations to only require bounded buffers.
% \TODO{Not sure if this restriction is useful, as arbitrary functions can still use however much memory and time as they want.}
